---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# wizehiver

[![CRAN status](https://www.r-pkg.org/badges/version/wizehiver)](https://cran.r-project.org/package=wizehiver)

Zengine from WizeHive is a platform that can organize the collection, review, and management of applications and data for grants and other business processes.

The goal of wizehiver is to build functionality to:

1. Input Zengine RESTful API token for Wizehive
2. Input available API resources
3. Execute API call
4. Process API request content
5. Extract data_frame objects

This package has no relationship or affiliation with, sponsorship or endorsement by Zengine.

## Installation

You can install the released version of wizehiver from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("wizehiver")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("ivelasq/wizehiver")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
## basic example code
```

---
Please note that this project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md).
By participating in this project you agree to abide by its terms.
